Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Update data availability scores and move text to discussion

However, data availability was mostly not available with 243 or 81.5% scoring '0' where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).

The most frequently cited software was SAS.
The remainder were mostly specialised software except for Microsoft Excel, tied for 9th (Table \@ref(tab:software-used)).

Unfortunately using our scoring method, most articles scored poorly for reproducibility or openness.
Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.

The software availability score was better as was the citing of software and versions used.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS.
It is interesting to note however, that with the popularity of Python that it does not even appear in our survey results whereas R was the fourth most commonly used software.

@@

>>>>

However, data availability was mostly not available with 361, or 80.2%, scoring '0' where the data was not available or mentioned in the article.
However, more articles, 44 or 9.8%, scored '3' than scored '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).

The most frequently cited software was SAS.
The remainder were mostly specialised software except for Microsoft Excel in a 3-way tie for 9th (Table \@ref(tab:software-used)).

Most articles, , scored poorly for reproducibility or openness.
Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.

The software availability score was better as was the citing of software and versions used.

@@

We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
We have based our scoring decisions on our own experiences in the field of plant pathology.
While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have access to them.
Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.

SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS.
It is interesting to note however, that with the popularity of Python that it does not even appear in our survey results whereas R was the fourth most commonly used software.
